Inference methods comparison for the simplified Naomi model

### 2023-05-01 src/naomi-simple_ks/ks.Rmd
Add ESS for Naomi outputs, close #29

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
adam <- readRDS("depends/adam.rds")
tmbstan <- readRDS("depends/tmbstan.rds")

@@

```{r}
time_taken <- data.frame(
  "TMB" = tmb$time,
  "aghq" = aghq$time,
  "adam" = adam$time,
  "tmbstan" = tmbstan$time
)

@@

time_taken

adam <- adam$adam
```

@@

We will write the `tmbstan` $\hat R$ and ESS for the particular parameter on each plot to help in deciding how seriously to take the MCMC results:

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter
```

@@

```{r}
ks_summary %>%
  pivot_longer(
    col = starts_with("KS"),
    names_to = "Method",
    values_to = "KS"
  ) %>%
  mutate(
    Method = fct_recode(Method,
      "adam" = "KS(adam, tmbstan)",
      "aghq" = "KS(aghq, tmbstan)",
      "TMB" = "KS(TMB, tmbstan)"
    )
  ) %>%
  group_by(Parameter) %>%
  mutate(
    par_num = case_when(
      max(index) > 1 ~ paste0(Parameter, "[", index, "]"),
      TRUE ~ Parameter
    )
  ) %>%
  ungroup() %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par_num")
  ) %>%
  ggplot(aes(x = ess, y = KS)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", color = "#56B4E9") +
    facet_grid(~ Method) +
    theme_minimal() +
    labs(x = "ESS", y = "KS(method, tmbstan)")
```

>>>>

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
adam <- readRDS("depends/adam.rds")
adam_time <- adam$time
adam <- adam$adam
tmbstan <- readRDS("depends/tmbstan.rds")

@@

```{r}
time_taken <- data.frame(
  "TMB" = tmb$time,
  "aghq" = aghq$time,
  "adam" = adam_time,
  "tmbstan" = tmbstan$time
)

@@

time_taken
```

@@

@@

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter

ks_summary %>%
  pivot_longer(
    col = starts_with("KS"),
    names_to = "Method",
    values_to = "KS"
  ) %>%
  mutate(
    Method = fct_recode(Method,
      "adam" = "KS(adam, tmbstan)",
      "aghq" = "KS(aghq, tmbstan)",
      "TMB" = "KS(TMB, tmbstan)"
    )
  ) %>%
  group_by(Parameter) %>%
  mutate(
    par_num = case_when(
      max(index) > 1 ~ paste0(Parameter, "[", index, "]"),
      TRUE ~ Parameter
    )
  ) %>%
  ungroup() %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par_num")
  ) %>%
  ggplot(aes(x = ess, y = KS)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", color = "#56B4E9") +
    facet_grid(~ Method) +
    theme_minimal() +
    labs(x = "ESS", y = "KS(method, tmbstan)")
```
